Simulation study in rectangular domain

### 2024-04-26 R/simulation_study/simulation_study_rect.Rmd
updates

```{r global variables}
#number of batch
N_BATCH=1

#number of individual tracks per batch
N_ID=3

@@

```{r plot estimates te ExpShore for one batch of low error samples}
xmin=list("theta"=-pi,"ExpShore"=1/2)
xmax=list("theta"=pi,"ExpShore"=1/0.3)
xlabel=list("ExpShore"="Distance to shore")
link=list("ExpShore"=(\(x) 1/x))
true_smooths=list("omega"=fomega_splines)
res=crcvm_rect_hf_ne1$BATCH1$get_all_plots(baseline=NULL,model_name="crcvm_rect_hf_ne1",xmin=xmin,xmax=xmax,
                                    xlabel=xlabel,link=link,show_CI="pointwise",true_smooths=true_smooths,save=TRUE)
res$fe_omega_theta_ExpShore
```

>>>>

```{r global variables}
#number of batch
N_BATCH=10

#number of individual tracks per batch
N_ID=6

@@

```{r plot estimates te ExpShore for one batch of low error samples}
xmin=list("theta"=-pi,"ExpShore"=1/2)
xmax=list("theta"=pi,"ExpShore"=1/0.3)
xlabel=list("ExpShore"="Distance to shore","theta"="Theta")
link=list("ExpShore"=(\(x) 1/x),"theta"=identity)
true_smooths=list("omega"=fomega_splines)
res=crcvm_rect_hf_ne1$BATCH1$get_all_plots(baseline=NULL,model_name="crcvm_rect_hf_ne1",xmin=xmin,xmax=xmax,
                                    xlabel=xlabel,link=link,show_CI="pointwise",true_smooths=true_smooths,save=FALSE)
res$fe_omega_theta_ExpShore
```
